\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{blindtext}
\usepackage{fontawesome}

%title creation
\title{Summary of the meeting with Dr. William D. Phillips}
\date{Octubre de 2017}
\author{David Silva Apango, \faTwitter DavidSA06\\ OSA-BUAP Student Chapter, \faTwitter OSA$\char`_$BUAP}
\begin{document}
\maketitle
The meeting began with a brief presentation from both Dr. William Phillips and Dr. Luis A. Orozco. Later, Dr. Phillips made a recommendation in attending congresses, one of them being in regard to the badges by saying that we dispense with the laces that hold them and instead use a clamp that is placed in the middle of the badge making a hole with a knife since being physical we should have one, this is done with the purpose of making the badge visible to other people by being able to choose the place where it is held. He also made a comment about the backpacks that are distributed in the congresses since we should not use the backpack of the current congress because it does not stand out among all the attendees, it would be best to keep the backpack and use one of the congress we attended previously.
\\
\\
Dr. Phillips motivated us to ask him questions through prizes that he would distribute to those who participated: Two cards containing the fundamental constants of physics, the first contained the currently recommended values while the second included the values that would be used in the next convention. 
\\
\\
The questions asked were :
\\
\\
\textbf{What opportunities do graduate students in the United States have after graduation for job opportunities?}
\\
\\
Both Doctors agree that something common among the academic staff of the universities is that they do not attract new students by telling them that the available places of work as researcher are reduced compared to the number of students who graduate, but this should not be a cause for concern because the The industry is currently requesting staff with a background in physics, mathematics, and engineering, especially in the area of quantum optics. In addition, Dr. Orozco mentioned that it is possible to work in the sale of laboratory equipment and material because the people in charge of the laboratories prefer salespeople who know their language and understand how the devices they sell work.
\\
\\
\textbf{How do you prepare your presentations?}
\\
\\
Dr. Phillips considers that he needs a lot of time to prepare his presentations, in case of giving a presentation on a topic that he had not presented before it takes approximately ten hours to prepare an hour of presentation and if the presentation is on a topic that he already presented then the preparation time decreases to two or three hours. Dr. Phillips acknowledges that that job is not his strong suit and that if someone is not dedicated enough to teach he should consider working in industry. 
\\
\\
\textbf{When you are a bachelor's or even a master's student, you approach a professor to ask him to give you a thesis topic that you can work on. How is the transition from being the student who asks a topic to being the teacher who proposes the topic and ideas?}
\\
\\
Can you tell me how a child learns to read? No. In general, people learn to do something because we see someone else doing it. If you smile at someone, they will learn to smile, if you talk to someone, they will learn to speak, if you read to someone they will learn to read, if you love someone, they will learn to love. The same goes for proposing ideas for research. If you propose ideas to the student and discuss them with him, he will eventually learn to do this. This maturity of the student almost always occurs when he is at the end of the doctorate or in the post-doctorate. The key is that each time you let the student take more initiative in proposing ideas.
\\
\\
\textbf{When you were a child, did you think you would win the Nobel Prize?}
\\
\\
Dr. Phillips told us that when he was a child he did not think about winning the Nobel Prize but that he considered reaching that goal at age 10 and as he progressed in his studies little by little he realized that this was a very distant goal and unrealistic. He also told us that when he was a child he was given a microscope in which he observed various objects in addition to creating his own chemistry set combining various cleaning supplies and that he is happy that he did not create a dangerous chemical reaction.
\\
\\
\textbf{How can you balance your scientific, family and social life?}
\\
\\
`` Not everything in life is physical, relationships with other people are very important. ”Dr. Phillips has been married for 47 years, he thinks that it is not worth compromising the family for scientific work. Dr. Phillips would prefer to return to his house to have dinner with his family and to tell his children a bedtime story that would win the Nobel Prize. ``It is very sad to see colleagues who are complete strangers in your house".
\\
\\
\textbf{Why did you decide to be a physicist?}
\\
\\
Because having a bad memory he decided to study something within the area of science, the problem was that chemistry is smelly, biology disgusting but physics was cleaner, he did not feel very ready to study mathematics but physics to have math was pleased.
\\
\\
\textbf{How can we attract children's attention to become more interested in science?}
\\
\\
Children can be attracted with colors, children should be allowed to touch the experiments because it is important for them to perceive the experiments with their own hands. No attempt should be made to change children's minds because out of their own curiosity they are heading towards science alone. Boring explanations should be avoided. It is also more important for people to see that the experiments are fun than to have a good understanding of the concepts. 
\\
\\
\textbf{Is there a relationship between science and the church?}
\\
\\
There is not, both are very different and are not related, since in science you can check hypotheses or you have evidence to prove the existence and in the church you do not know who God is or if in truth it exists or not, however it is important to believe in something as long as you know how to differentiate between the content offered by the bible and science. 
\\
\\
%\textbf{What was your worst mistake working in the lab?}
%\\
%\\
%After asking us not to laugh, he decided to tell us an anecdote in which he thought that working on magneto-optical traps could be interesting. After designing a very large and expensive device, he had it machined, this process took so long that as soon as the device arrived at the laboratory Dr. Phillips and his colleagues had already thought of several interesting topics which them keep busy so this device was stored while everyone was engaged in other occupations, later he decided to give it to other people who could put it to use. Dr. Phillips was not satisfied with telling this story because he did not learn much from this error, so he also told us about an experiment with optical molasses, these are an arrangement of three pairs of laser beams that counter-propagate perpendicularly to each other. Thanks to this arrangement they could cool a group of atoms that would oscillate very little but when turning off the lasers they thought that the atoms would violently detach from each other as if it were an explosion so a good way to study this behavior would be to place a detector above the optic molasse. When the lasers were turned off, the sensor did not detect anything despite the repetitions of the experiment. So they decided to leave the sensor down. On that occasion the sensor detected a huge number of atoms, it turned out that the group of atoms cooled more than expected and instead of exploding it fell directly to the sensor. In addition to the outcome of the experiment, Dr. Phillips learned not to focus on overthinking in the same way.
%\\
%\\
\textbf{How to win the Nobel Prize?}
\\
\\
People who are focused on winning a Nobel Prize will not win it, it is about continuing to study and learn, that in itself is a prize. With dedication could come a Nobel.
\\
\\
\textbf{What is the most important thing to consider in a career in science?}
\\
\\
The most important thing is to never lose interest and taste for what you do, you could have a job in which you have talent but with which you do not feel satisfied, that is why it is important to love the work you do.
\\
\\
\textbf{How to do science outreach for children?}
\\
\\
``The first thing to do when exposing anyone else is to lower expectations and show that science is fun. ”Under Dr. Phillips' consideration, it is better for people to have fun in a presentation than to fully understand the concepts: liquid nitrogen cooling the balloons are flat when they are removed from the container and it is at that moment that they are thrown to the public as if they were frisbees.
\\
\\
\textbf{Which are your hobbies?}
\\
\\
Photography and gospel singing in the Church choir.
\\
\\
\textbf{What is the hardest part of being a physical and a believer at the same time?}
\\
\\
There is no difficulty because science explains how the world works and opens your mind while the bible is a book that teaches you how to live with others, it is the word of God but it is not a science book. `` Even if there are people who are not respectful of religious beliefs, believers should respect others. ”In the end, he concluded by saying that when one goes to church he must open his heart, open his arms and open his mind.
\\
\\
\textbf{After winning the Nobel Prize, what are your goals in science?}
\\
\\
Continue giving lectures and carrying out simulations related to quantum physics.
\end{document}